---
title: "Advanced Techniques for Missing Data Handling"
author: "Vyshnavi Nammi, Dheeraj Reddy Podduturi, Ruchith Chippari, Anna Dragotta"
date: '`r Sys.Date()`'
format:
  html:
    code-fold: true
course: STA 6257 - Advanced Statistical Modeling
bibliography: references.bib # file contains bibtex for references
#always_allow_html: true # this allows to get PDF with HTML features
self-contained: true
execute: 
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

## Introduction

### **What is “Missing Data and Data Imputation”?**

Missing data refers to missing values for certain observations or
variables in a dataset. When collecting or recording data, it is not
uncommon to encounter situations where information is not available for
every individual or specific variable. Missing data can occur for
various reasons, such as non-response by participants, data entry
errors, equipment malfunctions, or simply because certain information
was not collected.

There are three main types of missing data:

1\. Missing Completely at Random (MCAR): Data missingness is unrelated
to observed and unobserved variables. In other words, the probability of
data being missing is the same for all observations.

2\. Missing at Random (MAR): The missingness is related to observed
variables but not to the values of the missing data itself. In this
case, the probability of data being missing can be predicted by other
variables in the dataset.

3\. Missing Not at Random (MNAR): The missingness is related to the
values of the missing data itself, even after considering observed
variables. This type of missing data can introduce bias and is often
more challenging to handle.

Handling missing data is crucial in statistical analysis because it can
lead to biased or inefficient results if not addressed properly.
Researchers employ various techniques, such as imputation methods, to
estimate or replace the missing values and ensure the validity and
reliability of their analyses. Imputation involves filling in missing
values with plausible estimates based on the observed data or using
statistical models to predict missing values.

Researchers need to be aware of the nature and mechanisms of missing
data in their datasets, as the choice of imputation method depends on
these factors. Ignoring missing data or handling it incorrectly can
impact the accuracy and generalizability of study findings.

Data imputation is a technique that aims to replace the missing data
with a substitute value. This technique can be applied when removing
data from the dataset is not feasible. Due to reasons such as a
reduction in the size of the dataset by a large extent. Reduction in
this way can also raise concerns for biases and incorrect analysis,
reduction can lead to distortion in the data variables and impact of the
final model with biases. The goal is to restore the complete dataset and
not lose any more of the data.

### Related work

The EHR has increasingly become used for data mining and analysis for a
variety of health conditions. However, due to irregular observation
times and innate uncertainties in a medical setting, the EHR datasets
are missing values. The EHR systems were not created in mind for
research. Researchers who do use this data may categorize this missing
data as missing completely at random, missing at random, or not missing
at random. (Marino et al. 2021) Regarding missing completely at random
(MCAR) data, all of the data points have the same odds to be missing.
Missing at random is attributable to things like the patient’s
condition, which means the missingness of the data is independent of the
value of the data. Not missing random data completely depends on the
value of the data. For each of these categories, the level of bias can
be different. (Jazayeri et al. 2020)

### Methods

 Some of the data imputation techniques are mentioned below.\
\
-   Next or Previous Value 

\-   K Nearest Neighbors

\-   Maximum or Minimum Value

\-   Missing Value Prediction

\-   Most Frequent Value

\-   Average or Linear Interpolation

\-   (Rounded) Mean or Moving Average or Median Value

\-   Fixed Value

\-   Rule-based imputation technique

\-   Random forest

Other imputation techniques consist of complete case analysis (CCA),
arbitrary value imputation, and frequent category imputation. Complete
case analysis involves directly removing the rows that have missing
data. This is also known as a listwise deletion. The assumption is the
data is missing at random (MAR). Arbitrary value imputation involves
handling both numerical and categorical variables. This technique
additionally includes grouping the missing values in a column and then a
value far from the range of the column. The values could be 999999,
-999999, missing or not defined. The assumption for this technique is
the data is not missing at random. Furthermore, frequent category
imputation is a technique that replaces the missing value with the
variable that has the highest frequency, meaning one replaces the value
with the mode of the column. This is also called mode imputation. The
assumption regarding this technique is that the data is missing at
random.

Another technique is multiple imputation. This imputation method is an
approach to missing data applied to common statistical packages.
Multiple imputation is used to allow for the uncertainty of the missing
data via creating many different plausible imputed datasets and
appropriately mixing results produced from each of them. The first step
is to create multiple copies of the dataset with the missing values
substituted via the imputed values since we can never know the true
values of the missing data, this imputation course of action should
capture fully all uncertainty in foreseeing the missing values by
inserting appropriate variability into the multiple imputed values. The
second stage is to utilize a standard statistical method. This method
should fit the model of interest for each of the datasets that
experienced imputation. (Sterne et al. 2009)

## Analysis and Results

The Titanic dataset contains information about the passengers on board
during the tragic event, categorizing them into three classes (1, 2, and
3). In total, there were 1309 people on board, with Class 1 having 200
people, Class 2 having 119 people, and Class 3 having 181 people. The
dataset provides valuable insights into the demographics, relationships,
and circumstances of the passengers aboard the Titanic during its
ill-fated journey. The missing information in certain fields may require
careful handling during analysis to ensure accurate and meaningful
results. The Titanic Ship Sunk dataset reveals missing information
across various fields. Specifically, records lack gender details for
certain passengers, instances exist where fare payments are not
recorded, cabin numbers are missing for some individuals, and
information about the port of embarkation is absent for others. Lifeboat
assignment details, identification numbers for recovered bodies, and
home or destination information are not provided for specific cases.
Addressing these gaps in data is imperative during analysis, and
researchers are advised to employ suitable methods like imputation or
exclusion based on research goals and the nature of the missing
information. It is crucial to thoroughly assess the impact of missing
data on results and draw conclusions accordingly for a comprehensive and
accurate interpretation of the dataset.

```{r, warning=FALSE, echo=T, message=FALSE}

# Install and load necessary packages
#install.packages("tidyverse")
#library(tidyverse)
#install.packages("readxl")
library(readxl)
```

```{r, warning=FALSE, echo=TRUE}

your_data <- read_excel("Titanic_dataset.xlsx")
#head(your_data)

# Define the columns for which you want to perform imputation
columns_to_impute <- c("pclass", "survived", "age", "sibsp", "parch", "fare")

missing_age <- sum(is.na(your_data$age))
missing_cabin <- sum(is.na(your_data$cabin))
missing_boat <- sum(is.na(your_data$boat))
missing_body <- sum(is.na(your_data$body))
missing_home_dest <- sum(is.na(your_data$home.dest))

# Print the counts of missing values
cat("Missing values in 'age':", missing_age, "\n")
Missing values in 'age': 263 
cat("Missing values in 'cabin':", missing_cabin, "\n")
Missing values in 'cabin': 1014 
cat("Missing values in 'boat':", missing_boat, "\n")
Missing values in 'boat': 823 
cat("Missing values in 'body':", missing_body, "\n")
Missing values in 'body': 1188 
cat("Missing values in 'home.dest':", missing_home_dest, "\n")
Missing values in 'home.dest': 564   

```

### Statistical Modeling

```{r}
 
```

### Conclusion

## References

1\) Jazayeri, A., Liang, O. S., & Yang, C. C. (2020, May 7). Imputation
of Missing Data in Electronic Health Records Based on Patients’
Similarities. https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8982680/\
 

2\) Marino, M., Lucas, J., Latour, E., & Heintzman, J. D. (2021, April).
Missing data in primary care research: importance, implications, and
approaches. https://www.ncbi.nlm.nih.gov/pmc/articles/PMC8243609/ 

3\) Mack, C. (2018). Types of missing data. Managing Missing Data in
Patient Registries: Addendum to Registries for Evaluating Patient
Outcomes: A User’s Guide, Third Edition \[Internet\].
https://www.ncbi.nlm.nih.gov/books/NBK493614/ 

4\) Jakobsen, J. C., Gluud, C., Wetterslev, J., & Winkel, P. (2017,
December 6). When and how should multiple imputations be used for
handling missing data in randomized clinical trials – a practical guide
with flowcharts - BMC Medical Research methodology. BioMed Central.
https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/s12874-017-0442-1 

5\) K Ross, R., Breskin, A., & Westreich, D. (2020, June). When Is a
Complete-Case Approach to Missing Data Valid? The Importance of
Effect-Measure Modification. National Library of Medicine .
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7705610/ 

6\) Sterne, J. A. C., White, I. R., Carlin, J. B., Spratt, M., Royston,
P., Kenward, M. G., Wood, A. M., & Carpenter, J. R. (2009, June 29).
Multiple imputation for missing data in epidemiological and clinical
research: Potential and pitfalls. The BMJ.
https://www.bmj.com/content/338/bmj.b2393#:\~:text=When%20it%20is%20plausible%20that,to%20be%20included%20in%20analyses 

7\) V. H. Umathe and G. Chaudhary, "Imputation methods for incomplete
data," 2015 International Conference on Innovations in Information,
Embedded and Communication Systems (ICIIECS), Coimbatore, India, 2015,
pp. 1-4, doi: 10.1109/ICIIECS.2015.7193063.

8\) W. Kim, W. Cho, J. Choi, J. Kim, C. Park, and J. Choo, "A Comparison
of the Effects of Data Imputation Methods on Model Performance," 2019
21st International Conference on Advanced Communication Technology
(ICACT), PyeongChang, Korea (South), 2019, pp. 592-599, doi:
10.23919/ICACT.2019.8702000.\
\
9) K. -F. Jea, C. -W. Hsu and L. -Y. Tang, "A Missing Data Imputation
Method With Distance Function," 2018 International Conference on Machine
Learning and Cybernetics (ICMLC), Chengdu, China, 2018, pp. 450-455,
doi: 10.1109/ICMLC.2018.8526985.

10\) Q. -T. Phan, Y. -K. Wu, Q. -D. Phan and H. -Y. Lo, "A Study on
Missing Data Imputation Methods for Improving Hourly Solar Dataset,"
2022 8th International Conference on Applied System Innovation (ICASI),
Nantou, Taiwan, 2022, pp. 21-24, doi: 10.1109/ICASI55125.2022.9774453.

11\) K. Chungnoy and P. Songmuang, "Missing Values Imputation Framework
for Mixed Datasets," 2023 IEEE International Conference on Cybernetics
and Innovations (ICCI), phetchaburi, Thailand, 2023, pp. 1-5, doi:
10.1109/ICCI57424.2023.10111846.

12\) K. Tripathi, H. Saini and G. Rathee, "Missing Values Imputation in
Food Consumption: An Analytical Study," 2021 6th International
Conference on Signal Processing, Computing and Control (ISPCC), Solan,
India, 2021, pp. 303-307, doi: 10.1109/ISPCC53510.2021.9609371.

13\) Nurzaman, T. Siswantining, S. M. Soemartojo and D. Sarwinda,
"Application of Sequential Regression Multivariate Imputation Method on
Multivariate Normal Missing Data," 2019 3rd International Conference on
Informatics and Computational Sciences (ICICoS), Semarang, Indonesia,
2019, pp. 1-6, doi: 10.1109/ICICoS48119.2019.8982423.

14\) W. Yu, W. Zhu, G. Liu, B. Kan, T. Zhao and H. Liu, "Cluster-Based
Best Match Scanning for Large-Scale Missing Data Imputation," 2017 3rd
International Conference on Big Data Computing and Communications
(BIGCOM), Chengdu, China, 2017, pp. 232-238, doi:
10.1109/BIGCOM.2017.48.

15\) C. Yan, J. Yuan, Z. Ye, and Z. Yang, "A Discrete Missing Data
Imputation Method Based on Improved Multi-layer Perceptron," 2021 11th
IEEE International Conference on Intelligent Data Acquisition and
Advanced Computing Systems: Technology and Applications (IDAACS),
Cracow, Poland, 2021, pp. 480-484, doi:
10.1109/IDAACS53288.2021.9661028.

16\) L. Ehrlinger, T. Grubinger, B. Varga, M. Pichler, T. Natschläger
and J. Zeindl, "Treating Missing Data in Industrial Data Analytics,"
2018 Thirteenth International Conference on Digital Information
Management (ICDIM), Berlin, Germany, 2018, pp. 148-155, doi:
10.1109/ICDIM.2018.8846984.

17\) E. F. Akmam, T. Siswantining, S. M. Soemartojo, and D. Sarwinda,
"Multiple Imputation with Predictive Mean Matching Method for Numerical
Missing Data," 2019 3rd International Conference on Informatics and
Computational Sciences (ICICoS), Semarang, Indonesia, 2019, pp. 1-6,
doi: 10.1109/ICICoS48119.2019.8982510.

18\) C. F. Usanmaz, M. E. White, M. Valancius and M. D. Wang, "An
Expansion for Automated Cardiac Anomaly Detection Frameworks with
Multimodal Missing Data Imputation," 2021 IEEE EMBS International
Conference on Biomedical and Health Informatics (BHI), Athens, Greece,
2021, pp. 1-5, doi: 10.1109/BHI50953.2021.9508517.
